Fig 2

### 2020-08-07 analysis/figure-2-new.Rmd
small edits

```{r fig2-new, fig.width=7, fig.height=7}

a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) + labs(subtitle = " ")

b <- makebargraph(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 4800, comparisonlabelscontrol) +
  labs(x = "Control versus all other reproductive and parental stages")

c <- makebargraph(DEGbldg, "hypothalamus", "DEGs w/ + LFC", 0, 480, comparisonlabelsbldg) +
  labs(x = "Nest-building versus all other parental stages")
d <- makebargraph(DEGchar, "hypothalamus","DEGs w/ + LFC", 0, 1700, comparisonlabelscharnobldg) +
  labs(x = "Comparison of sequential parental stages")

e <- makebargraph(DEGbldg, "pituitary", "DEGs w/ + LFC", 0, 2200, comparisonlabelsbldg)

f <- makebargraph(DEGchar, "pituitary","DEGs w/ + LFC", 0, 1500, comparisonlabelscharnobldg)

g <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2800, comparisonlabelsbldg) 
h <- makebargraph(DEGchar, "gonad","DEGs w/ + LFC", 0, 1200, comparisonlabelscharnobldg)

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("A Hypothalamus", " " ), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1,1))
ef <- plot_grid(e,f,rel_widths = c(1,1),
                labels = c("B Pitutary"), label_size = 8 ,hjust = 0)
gh <- plot_grid(g,h,rel_widths = c(1,1), 
                labels = c("C Gonads"), label_size = 8, hjust = 0)

@@

png("../figures/fig2-new-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig) # Make plot
dev.off()

>>>>

```{r fig2-new, fig.width=7.25, fig.height=7.25}
a <- plot.volcano("hypothalamus", sexlevels,  "control_bldg") + 
  facet_wrap(~sex) + labs(subtitle = " ")
b <- makebargraph(DEGcontrol, "hypothalamus","DEGs w/ + LFC", 0, 5000, comparisonlabelscontrol) +
  labs(title = " ",
       subtitle = "Control versus all other reproductive and parental stages")

c <- makebargraph(DEGbldg, "hypothalamus", "DEGs w/ + LFC", 0, 490, comparisonlabelsbldg) +
  labs(subtitle = "Nest-building versus all other parental stages")
d <- makebargraph(DEGchar, "hypothalamus", NULL, 0, 1800, comparisonlabelscharnobldg) +
  labs(subtitle = "Comparison of sequential parental stages")

e <- makebargraph(DEGbldg, "pituitary", "DEGs w/ + LFC", 0, 2300, comparisonlabelsbldg)

f <- makebargraph(DEGchar, "pituitary",NULL, 0, 1600, comparisonlabelscharnobldg)

g <- makebargraph(DEGbldg, "gonad", "DEGs w/ + LFC", 0, 2900, comparisonlabelsbldg) 
h <- makebargraph(DEGchar, "gonad", NULL, 0, 1200, comparisonlabelscharnobldg)

ab <- plot_grid(a,b,rel_widths = c(1,2.5), 
                labels = c("A Hypothalamus"), label_size = 8, hjust = 0)
cd <- plot_grid(c,d,rel_widths = c(1.1,1), align = "h")
ef <- plot_grid(e,f,rel_widths = c(1.1,1), align = "h",
                labels = c("B Pitutary"), label_size = 8 ,hjust = 0)
gh <- plot_grid(g,h,rel_widths = c(1.1,1), align = "h",
                labels = c("C Gonads"), label_size = 8, hjust = 0)

@@

png("../figures/fig2-new-1.png", width = 7, height = 7, 
    units = 'in', res = 300)
plot(fig) 
dev.off()
